---
title: "MATH4753JEREMYSMITHLab4S3-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MATH4753JEREMYSMITHLab4S3-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753JEREMYSMITHLab4S3)
```

## K = 1

### Task 1

Build an S3 constructor function that takes two arguments, $x$ and $k$ and returns the values of $x$, the new variable $inout$, and $k$.

```{r task 1.1}
df1 <- mybiplot(epagas$MPG, 1)
head(df1$result_table)
```

### Task 2

Plot the data in a histogram with respect to $inout$.

```{r task 1.2]}
df1$plot
```

### Task 3

Build a summary table that provides descriptive statistics for the data.

```{r task 1.3}
df1$summary
```

## k = 2

### Task 1

Build an S3 constructor function that takes two arguments, $x$ and $k$ and returns the values of $x$, the new variable $inout$, and $k$.

```{r task 2.1}
df2 <- mybiplot(epagas$MPG, 2)
head(df2$result_table)
```

### Task 2

Plot the data in a histogram with respect to $inout$.

```{r task 2.2]}
df2$plot
```

### Task 3

Build a summary table that provides descriptive statistics for the data.

```{r task 2.3}
df2$summary
```

## k = 3

### Task 1

Build an S3 constructor function that takes two arguments, $x$ and $k$ and returns the values of $x$, the new variable $inout$, and $k$.

```{r task 3.1}
df3 <- mybiplot(epagas$MPG, 3)
head(df3$result_table)
```

### Task 2

Plot the data in a histogram with respect to $inout$.

```{r task 3.2]}
df3$plot
```

### Task 3

Build a summary table that provides descriptive statistics for the data.

```{r task 3.3}
df3$summary
```
